BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-18 tex/1-intro.tex
Merge Vangelis comments

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, political or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}. The need to preserve this volatile communication medium is nowadays very clear.

@@

A key characteristic of blogs which differentiates them from regular websites is their association with web feeds. Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs. Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata. Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest previous content.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions and Overview}
We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing blogs, extracting their content and monitoring their updates. Our contributions are in particular:

\begin{itemize}
  \item We present a new algorithm to build extraction rules from web feeds. We then derive an optimized reformulation tied to a particular string similarity metric and show that this reformulated algorithm has a linear time complexity.
  \item We show how to use this algorithm for blog article extraction and how it can be adapted to authors, publication dates and comments.
  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
  \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them. This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time. A comparison is made with three state-of-the-art article extraction algorithms.
\end{itemize}

@@

>>>>

Blogs disappear every day \cite{johnson2008blogs}. Losing data is obviously undesirable, but even more so when this data has historic, political or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}. The need to preserve this volatile communication medium is nowadays very clear.

@@

A key characteristic of blogs which differentiates them from regular websites is their association with web feeds \cite{lindahl2003weblogs}. Their primary use is to provide a uniform subscription mechanism, thereby allowing users to keep track of the latest updates without the need to actually visit blogs. Concretely, a web feed is an XML file containing links to the latest blog posts along with their articles (abstract or full text) and associated metadata \cite{board2007rss}. Nevertheless, while web feeds essentially solve the question of update monitoring, their limited size makes it necessary to download blog web pages in order to harvest previous content.

\TODO{
  After writing the first sentece, you should write what are our aims in this work. (keep it in the same paragraph).\\
  \\
  Our main objective in this work are to create better algorithms and techniques for blog content extraction. (maybe you want to write something extra here+++, then, continue with the contributions:\\
  \\
  Our contributions can be summarised as follows:
}

We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates. Our contributions can be summarized as follows:

\begin{itemize}
  \item We present a new algorithm to build extraction rules from web feeds. We then derive an optimized reformulation tied to a particular string similarity metric and show that this reformulated algorithm has a linear time complexity.
  \item We show how to use this algorithm for blog article extraction and how it can be adapted to authors, publication dates and comments.
  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
  \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them. This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
  \item We evaluate the content extraction and execution time of our algorithm against three state-of-the-art web article extraction algorithms.
\end{itemize}

\TODO{This part should be removed and the information contained here should go before the bullets (where you say what are our aims)}

@@

The rest of the paper is organized as follows. In Section 2, we present related work on web crawlers and web data extraction. In Section 3, we define our algorithms and in Section 4 we explain the techniques we used for implementation. We evaluate our algorithms and present results in Section 5. Finally, in Section 6 we present our conclusions and future work.

### 2014-01-18 tex/3-algorithms.tex
Merge Vangelis comments

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of throughout a blog. Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.

@@

% observations when working with blogs
Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 blog posts \cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in web feed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
\label{contentextraction}

@@

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
\hyperref[extractionrulesandstringsimilarity]{Subsection~\ref*{extractionrulesandstringsimilarity}} % Waiting for \Autoref{}...
defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing. Finally, \autoref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

>>>>

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules which are applicable to all blog posts. Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

% observations when working with blogs
Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure,
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog.
\end{enumerate}
Web feeds usually contain about 20 blog posts \cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in web feed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction overview}
\label{contentextraction}

@@

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
\hyperref[extractionrulesandstringsimilarity]{Subsection~\ref*{extractionrulesandstringsimilarity}} % Waiting for \Autoref{}...
defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programming. Finally, \autoref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

### 2014-01-18 tex/4-techniques.tex
Merge Vangelis comments

This section gives an overview of the different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture is then discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Finally we talk about the design choices we made in view of a large scale deployment.

@@

% blog post identification
Given an URL entry point to a website, the default Scrapy behavior traverses all the pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not. Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed. This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur). In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.

@@

% Distance-Weighted k-Nearest-Neighbor
The idea is to give high priority to URLs which are believed to point to pages with links to blog posts. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.

@@

Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high-level point of view, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
%
where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator. By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

>>>>

This section provides an overview of the crawler system architecture and the different techniques we used. The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. Finally, we talk about the design choices we made in view of a large scale deployment.

@@

% blog post identification
Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not. Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed. This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur). In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.

@@

% Distance-Weighted k-Nearest-Neighbour
The idea is to give high priority to URLs which are believed to point to pages with links to blog posts. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.

@@

Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high-level point of view, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
%
where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the power set operator. By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

### 2014-01-18 tex/5-evaluation.tex
Merge Vangelis comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate article and title extraction from blog posts we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively. These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}). \autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.

@@

On our test dataset \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page. On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules. Therefore, results showen in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate article and title extraction from blog posts we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively. These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}). \autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts from 230 blogs obtained from the Spinn3r dataset \cite{burton2011}.

@@

On our test dataset \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page. On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules. Therefore, results showed in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as an evidence that our approach is more suitable when working with blogs.

@@

\TODO{\\
  > what is the initial computation time? It would be good to know and have some numbers.\\\\
  The initial computations is the time we spend to go from 0 to 1 processed blog posts on the graph, which includes processing the web feed and the 15 pages it contains. I have the exact numbers in the repo but it's basically the tiny white space we see on the graph, ~1/8 second.
}

### 2014-01-18 tex/6-conclusion-and-future-work.tex
up
minor
Merge Vangelis comments

% Future work, hybrid algos
Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates. Even if the overall performance of our approach is better than those of comparable projects (as shown in the evaluation), there are still a few cases where other techniques managed to extract data and we did not. This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performance.

% Deployment on a distributed architecture
Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system. This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck. Crawler greatly benefits from the use of multiple Internet access points which makes them natural candidates for distributed computing. We intend to explore this opportunities in our future work.

% Conclude the conclude
To open up further possibilities\comment{rephrase?}, the crawler presented in this paper is available under the MIT license from the project's website \cite{blogforevercrawler}.

>>>>

% Future work, hybrid algos
Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.

\TODO{\\
  > You didn't say anything about this in the evaluation, did you?
  Either present some numbers about it or remove this thing from the conclusions.
  \\\\
  I think I will simply rephrase it with less precisions, but the idea is that there is some overlap between the 7\% of posts we fail to extract and the 88.1\% of posts extracted by readability, likely in the order of 7\% * 88.1\% as the conditions of failure are completely independent.
}

Even if the overall performance of our approach is better than those of comparable projects (as shown in the evaluation), there are still a few cases where other techniques managed to extract data and we did not. This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performance.

% Deployment on a distributed architecture
Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system. This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck. Crawler greatly benefits from the use of multiple Internet access points which makes them natural candidates for distributed computing. We intend to explore these opportunitie in our future work.
